\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[margin=.75in]{geometry}  % Sets the margins

\usepackage{color}
 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\title{5200 CPU 3}
\author{Matthew Cather}
\date{March 2019}

\begin{document}

\maketitle

For this section of the project I finished the integration of the CPU top. This is composed of three parts: the decoder, the control unit, and the data-path. These were all written in SystemVerilog with the ultimate goal of synthesis and implementation of the CPU. Most of the simple register and Multiplexer modes were dropped because they were one lines in SystemVerilog.

For assembly encoding a simple assembler was written and attached at the end. The assembled utilized an ISA specification configuration that is also attached.

testing listing were omitted because they are hard to interpret. More readable testing results are attached.

Models are presented in the following format, model and testbench together with the listing result at the end. This was done for brevity.

\tableofcontents
\clearpage

\section{Decoder File}
\lstinputlisting[language=verilog]{components/Control/Decoder.sv}
\subsection{Test-bench}
\lstinputlisting[language=python]{components/Control/Decoder_test.py}

\section{Control unit}
\lstinputlisting[language=verilog]{components/Control/ControlUnit.sv}
\subsection{Test-bench}
\lstinputlisting[language=python]{components/Control/ControlUnit_test.py}

\section{Datapath unit}
\lstinputlisting[language=verilog]{components/Datapath/Datapath.sv}
\subsection{Test-bench}
\lstinputlisting[language=python]{components/Datapath/Datapath_test.py}

\section{Testbench Results}
\lstinputlisting{top.txt}


\section{Assembler}
\lstinputlisting[language=python]{assembler.py}
\section{ISA.yaml}
\lstinputlisting{isa.yaml}

\end{document}
